---
title: "Fusing multiple enrichment results generated from different databases"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fusing multiple enrichment results generated from different databases}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(EnrichGT)
```

# Summary

The default setting of `clusterProfiler` only supports enrichment from a single database (which is reasonable for accurate p-values). However, a single database often lacks sufficient coverage. Frequently, we need to cross-reference GO, KEGG, Reactome, and other databases. EnrichGT offers a method to integrate results from multiple database sources, providing us with a coherent way to interpret these results through `gt` presentation.

# Example1: Merging ORA results from GO + KEGG

First, we should generate a `list` containing different enrichment results. 

```{r}
suppressPackageStartupMessages({library(tidyverse)
library(clusterProfiler)
library(org.Hs.eg.db)})
data(geneList, package="DOSE")
gene <- names(geneList)[abs(geneList) > 2]
ego <- enrichGO(gene          = gene,
                universe      = names(geneList),
                OrgDb         = org.Hs.eg.db,
                ont           = "CC",
                pAdjustMethod = "BH",
                pvalueCutoff  = 0.01,
                qvalueCutoff  = 0.05,
                readable      = TRUE)
kk <- enrichKEGG(gene         = gene,
                 organism     = 'hsa',
                 pvalueCutoff = 0.05)

ora_result_list<-list(ego,kk)

```

We can see the list contains GO and KEGG results. 

```{r}
str(ora_result_list,max.level = 1)
```

Next, simple bring it to `EnrichGT()`, like regular enrichment objects. 

```{r}
ora_result_list_egt<-ora_result_list |> EnrichGT()
ora_result_list_egt@gt_object
```


# Example2: Merging GSEA results from GO + KEGG

Like before, we should generate a `list` contains 2 GSEA results. 

```{r}
ego3 <- gseGO(geneList     = geneList,
              OrgDb        = org.Hs.eg.db,
              ont          = "CC",
              minGSSize    = 100,
              maxGSSize    = 500,
              pvalueCutoff = 0.05) |> setReadable(OrgDb = org.Hs.eg.db,keyType = "ENTREZID")
kk3 <- gseKEGG(gene         = geneList,
                 organism     = 'hsa',
                 pvalueCutoff = 0.05) |> setReadable(OrgDb = org.Hs.eg.db,keyType = "ENTREZID")
gsea_result_list<-list(ego3,kk3)
str(ora_result_list,max.level = 1)
```

Then, go to `EnrichGT()`! 

```{r}
gsea_result_list_egt<-gsea_result_list |> EnrichGT()
gsea_result_list_egt@gt_object
```


# Session Info

```{r}
sessioninfo::session_info()
```

